Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-15 main.tex
Added proper acknowledgements

>>>>

We warmly thank all the children, teachers and staff of the International School
of Geneva, the Institut Florimont and the Haut-Lac school for their
participation and support. We express our great gratitude to Anne Gossin and [TBD] for
inviting us to their surgery, for their involvement in the experiments and for
bearing with our disruptive robots. And finally, we want to say a very special \emph{Thank
you!} to Vincent, Thomas, Valérie, Émilien, Mathieu, Johan, Nicolas, Antoine,
Adèle and Marie: by spending several hours being patient teachers for our
robots, you have paved the way for what may become tomorrow a new way of
learning how to deal with all these letters and words!
